\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/impl.tex
S5

\section{Implementation}
\label{sec:impl}
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
library~\cite{aby}. We set the security paramenter to 128 and use OT extension-based arithmetic multiplication triples generation. ABY provides facilities to use multiple threads\footnote{The protocol has an offline phase and an online phase. Although multiple threads can be used in the offline phase, the online phase is single threaded.} and we use at most four threads in our evaluation.

The current language implementation supports the following operators:
addition, subtraction, multiplication, division by powers of two, left shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary negation,
bitwise-negation, logical-(not, and, or, xor), and comparisons (less than, greater than, equality).
Because of their high cost, integral division and floating-point operators are not supported natively by \tool.
However, we have implemented integral division in 30 lines of \tool and floating-point support in
ABY is under active development~\cite{ddkssz15}.

Some of our benchamrks require accessing arrays at secret location.
For example, consider the expression $A[x]$ where $A$ is an array of size 2 and $x$ is shared.
\tool enforces the array indices to be public. The developer expresses this functionality in \tool
as $x > 0 ? A[1] : A[0]$. In general, a secret access to an array of size $2^n$ requires $2^{n}-1$ multiplexers in \tool.

 Secure code partitioning currently requires a manual step.
In particular, the developer needs to decompose a program $P$ into $P_1||\ldots||P_k$ manually (Section~\ref{sec:pipe}). Then \tool generates $Q_1||\ldots||Q_k$ automatically.
Automating the decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave the construction of such
an analysis as future work.

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to check the verification conditions required
to prove that the array indices remain in bound ($\Gamma\vDash e < n$ in {\sc T-Read}, Figure~\ref{fig:compile}). The solver takes less
than a minute on our largest benchmark.
The type label is assigned conservatively in  {\sc T-Decl}.
Only the variables that govern the control flow, i.e., variables
in if-conditions and for-loops are assigned public labels.
All other variables are assigned arithmetic labels (and can later be coerced to boolean).
In the future, we would like to explore more intelligent strategies for label assignment.

The compilation rules of Figure~\ref{fig:compile} can introduce redundant coercions from arithmetic to
boolean  and vice versa.
The \tool compiler performs several optimizations to reduce these.
For example, on each coercion, \tool memorizes the pair of arithmetic share and boolean share involved in the coercion.
\tool invalidates such pairs when the variables corresponding to the shares are overwritten by assignments.
In subsequent coercions, \tool  reuses valid pairs (if available) instead of recomputing them afresh.

>>>>

\section{Implementation}
\label{sec:impl}
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. We use the default ABY configuration for our
experiment \footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the
protocol), we leverage the support and use at most four threads in our
evaluation.

Our current implementation supports the following operators:
addition, subtraction, multiplication, division by powers of two, left
shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary
negation, 
bitwise-negation, logical-(not, and, or, xor), and comparisons (less
than, greater than, equality). 
Because of their high cost, integral division and floating-point
operators are not supported natively by \tool. 
However, we have implemented integral division in 30 lines of \tool,
while the floating-point support in ABY is under active
development~\cite{ddkssz15}.

Some of our benchamrks require accessing arrays at secret
indices. While \tool enforces the array indices to be
public, secret indices can be encoded in \tool using multiplexers.
For example, consider the expression $A[x]$ where $A$ is an array of
size 2 and $x$ is secret-shared. The developer can expresse
this functionality in \tool as $\cond{x > 0}{A[1]}{A[0]}$. In general,
a secret access to an array of
size $2^n$ requires $2^{n}-1$ multiplexers in \tool.

 Secure code partitioning currently requires a manual step.
In particular, the developer needs to decompose a program $P$ into
$P_1||\ldots||P_k$ manually (Section~\ref{sec:pipe}). Then \tool
generates $Q_1||\ldots||Q_k$ (the sub-programs with appropriate
wrappers) automatically.
Automating the decomposition step requires an analysis that can 
statically estimate the resource usage of an \tool program. We leave
the construction of such an analysis as future work.

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($\Gamma\vDash e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}})),
Figure~\ref{fig:compile}). We take the \tool source program and
translate it as an input to the solver. The solver takes less
than a minute on our largest benchmark.

Our implementation assigns the type labels (rule~{\sc{T-Decl}})
conservatively. Only the variables that govern the control flow, i.e.,
variables in \kw{if}-conditions and \kw{for}-loop counters are
assigned public labels.
All other variables are assigned arithmetic labels (that can later be
coerced to boolean).
We leave a more sophisticates type inference procedure for future work.

The compilation rules of Figure~\ref{fig:compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
The \tool implementation performs several optimizations to reduce
these coercions.
For example, on each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of recomputing them afresh.
